\textbf{ANALYSIS OF \\ MACHINE LEARNING \\ APPLIED TO BOARD GAMES}

### 2022-12-01 doc/paper.tex
small changes to paper
added sections to paper

\begin{abstract}
In late 2017 DeepMind announced a groundbreaking system in a preprint \cite{alphazero} and the results were astonishing. The system was called AlphaZero and utilized \emph{artificial neural networks} in combination with \emph{heuristic algorithms} in order to teach itself the game chess without any proprietary knowledge. After approximately 9 hours it was able to beat the strongest hand-crafted engines, such as Stockfish and it had learned centuries of human knowledge of chess. In this paper we aim to study the effectiveness of different \emph{neural networks} and \emph{heuristic algorithms} such as the one used in AlphaZero. More precisely, we intend to analyze the efficiency of those networks and algorithms in combination with varying \emph{optimizations, parameters, hyperparameters} and \emph {architectures} applied to the classic games \emph{Connect Four} and \emph{Othello}.

\vskip 0.8cm

@@

@@

\nomenclature{$\upepsilon$}{probability of taking a random action in an $\upepsilon$\hyp greedy policy}
\nomenclature{$\argmin_x f(x)$}{\{$x \mid f(x) = \min_{x'} f(x')$\}}
\nomenclature{$\argmax_x f(x)$}{\{$x \mid f(x) = \max_{x'} f(x')$\}}
\nomenclature{$\leftarrow$}{assignment}
\nomenclature{$\upgamma$}{discount-rate parameter}

\nomenclature{$\textnormal{s, s'}$}{states}

@@

\section{Introduction}

@@

>>>>

\begin{abstract}
In October 2017 DeepMind announced an artificial intelligence in a preprint \cite{alphazero} that was called AlphaTensor. It utilized \emph{artificial neural networks} in combination with \emph{heuristic algorithms} in order to solve the unsolved problem of finding faster algorithms for matrix multiplication. AlphaTensor was succesful and has shed light on the process of finding new algorithms. In this paper we aim to study the effectiveness of different \emph{neural networks} and \emph{heuristic algorithms} such as the one used in AlphaTensor. More precisely, we intend to analyze the efficiency of those networks and algorithms in combination with varying \emph{optimizations, parameters, hyperparameters} and \emph {architectures} applied to the classic games \emph{Connect Four} and \emph{Othello}.

\vskip 1cm

@@

\section*{Preface}
\addcontentsline{toc}{section}{Preface}

@@

\nomenclature{$\argmin_x f(x)$}{\{$x \mid f(x) = \min_{x'} f(x')$\}}
\nomenclature{$\argmax_x f(x)$}{\{$x \mid f(x) = \max_{x'} f(x')$\}}
\nomenclature{$\leftarrow$}{assignment}
\nomenclature{$P(a \mid b)$}{probability of a given b}

@@

@@

\section{Games}
\subsection{Connect Four}
\subsection{Othello}

\section{Deep Learning}

\subsection{Introduction}

\subsection{Basic Architecture of Neural Networks}
\subsubsection{Perceptron}
\subsubsection{Fully Connected Neural Network}

\subsection{Backpropagation}
\subsubsection{Gradient Descent}
\subsubsection{Loss Function}

\subsection{Complications with Neural Network Training}
\subsubsection{Overfitting}
\subsubsection{Vanishing and Exploding Gradient}
\subsubsection{Difficulties in Convergence}
\subsubsection{Local Optima}
\subsubsection{Computational Challenges}

\subsection{Training Neural Networks}
\subsubsection{Backpropagation in Detail}
\subsubsection{Preventing Extreme Gradients}
\subsubsection{Gradient Descent Strategies}

\subsection{Generalizing Neural Networks}

\subsection{Convolutional Neural Network}
\subsubsection{Historical Background}
\subsubsection{Architecture of a Convolutional Network}
\subsubsection{Training a Convolutional Network}
\subsubsection{Applications of Convolutional Networks}

\section{Reinforcement Learning}

\subsection{Introduction}

\subsection{Monte Carlo Tree Search}
\subsubsection{Upper Confidence Bound}

\section{Heuristic Algorithms}
\subsection{MiniMax}
